Lactate transport inhibition therapeutically reprograms fibroblast

### 2024-04-25 manuscript/manuscript.qmd
fix grant support and add email addresses

authors:
- name: David R. Ziehr
  affiliations: 
  - ref: bwh
  - ref: mgh
  - ref: hms
- name: Fei Li
  affiliations:
  - ref: bwh
  - ref: hms
- name: K. Mark Parnell
  affiliations:
  - ref: vettore
- name: Nathan M. Krah
  affiliations:
  - ref: utah_gen
  - ref: utah_biochem
- name: Kevin J. Leahy 
  affiliations:
  - ref: bwh
- name: Christelle Guillermier
  affiliations:
  - ref: bwh
  - ref: hms
- name: Jack Varon
  affiliations: 
  - ref: bwh
  - ref: hms
- name: Rebecca M. Baron
  affiliations:
  - ref: bwh
  - ref: hms
- name: Bradley A. Maron
  affiliations:
  - ref: umd
  - ref: ihc
- name: Nancy J. Philp
  affiliations:
  - ref: tj
- name: Lida P. Hariri
  affiliations: 
  - ref: hms
  - ref: mgh_path
- name: Edy Y. Kim
  affiliations:
  - ref: bwh
  - ref: hms
- name: Matthew L. Steinhauser
  affiliations:
  - ref: pitt
  - ref: upmc
- name: Rachel S. Knipe
  affiliations:
  - ref: mgh
  - ref: hms
- name: Jared Rutter
  affiliations:
  - ref: utah_biochem
  - ref: utah_hhmi
- name: William M. Oldham
  affiliations:
  - ref: bwh
  - ref: hms
  email: woldham@bwh.harvard.edu
  corresponding: true

@@

* National Institutes of Health grant R01GM987654 (WMO)
* Brigham and Women's Hospital Research Institute (WMO)
* American Lung Association grant DA-827785 (EYK)
* BWH Bell Family Award (EYK)
* National Institutes of Health grant R01HL152075 (LH)
* National Institutes of Health grant T32HL007633 (JV)

>>>>

authors:
- name: David R. Ziehr
  affiliations: 
  - ref: bwh
  - ref: mgh
  - ref: hms
  email: dziehr@mgb.org
- name: Fei Li
  affiliations:
  - ref: bwh
  - ref: hms
  email: feli@bwh.harvard.edu
- name: K. Mark Parnell
  affiliations:
  - ref: vettore
  email: markparnell1@gmail.com
- name: Nathan M. Krah
  affiliations:
  - ref: utah_gen
  - ref: utah_biochem
  email: Nathan.Krah@hci.utah.edu
- name: Kevin J. Leahy 
  affiliations:
  - ref: bwh
  email: kjleahy@bwh.harvard.edu
- name: Christelle Guillermier
  affiliations:
  - ref: bwh
  - ref: hms
  email: cguillermier@bwh.harvard.edu
- name: Jack Varon
  affiliations: 
  - ref: bwh
  - ref: hms
  email: varon.jack@gmail.com
- name: Rebecca M. Baron
  affiliations:
  - ref: bwh
  - ref: hms
  email: rbaron@bwh.harvard.edu
- name: Bradley A. Maron
  affiliations:
  - ref: umd
  - ref: ihc
  email: BMaron@som.umaryland.edu
- name: Nancy J. Philp
  affiliations:
  - ref: tj
  email: Nancy.Philp@jefferson.edu
- name: Lida P. Hariri
  affiliations: 
  - ref: hms
  - ref: mgh_path
  email: lhariri@mgh.harvard.edu
- name: Edy Y. Kim
  affiliations:
  - ref: bwh
  - ref: hms
  email: ekim11@bwh.harvard.edu
- name: Matthew L. Steinhauser
  affiliations:
  - ref: pitt
  - ref: upmc
  email: msteinhauser@pitt.edu
- name: Rachel S. Knipe
  affiliations:
  - ref: mgh
  - ref: hms
  email: rknipe@mgh.harvard.edu
- name: Jared Rutter
  affiliations:
  - ref: utah_biochem
  - ref: utah_hhmi
  email: rutter@biochem.utah.edu
- name: William M. Oldham
  affiliations:
  - ref: bwh
  - ref: hms
  email: woldham@bwh.harvard.edu
  corresponding: true

@@

* National Institutes of Health grant R01HL167718 (WMO)
* Brigham and Women's Hospital Research Institute (WMO)
* American Lung Association grant DA-827785 (EYK)
* BWH Bell Family Award (EYK)
* National Institutes of Health grant R01HL152075 (LH)
* National Institutes of Health grant T32HL007633 (JV)
